Dark Control:\\ A Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-09-17 paper/paper.tex
more

At the current step $k$, computing an optimal parameter update then corresponds to
finding the model parameters $\theta_{k}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal D}[(\tilde{Q}(s, a|\theta) - \tilde{Q}(s',a'|\theta^Q_{k}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal D}\left[\frac{1}{2}(\tilde{Q}(s, a|\theta_{k}) - y_k)^2\right],
  \label{eq:oracle}
\end{equation}
where $y_k$ is defined in \eqref{eq:bellman}.
% \textbf{We still may need to explain y in the formula with one sentence.}
A recently proposed, practically successful alternative approach
\citep{mnih2015,silver2016mastering} is to learn this
representation using a deep neural-network model, leading to the
so-called \textit{deep Q-learning} family of methods which
likely are state-of-the-art in RL.
The set of model parameters $\theta$ that instantiate the non-linear interactions
between layers of the artifical neural network
may find a neurobiological correspondence in the adaptive strengths of axonal
connections between neurons from the different levels
of the neural processing hierarchy
\citep{mesulam1998sensation, taylor2015global}.

>>>>

At the current step $k$, computing an optimal parameter update then corresponds to
finding the model parameters $\theta_{k}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal D}[(\tilde{Q}(s, a|\theta) - \tilde{Q}(s',a'|\theta^Q_{k}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal D}\left[\frac{1}{2}(\tilde{Q}(s, a|\theta_{k}) - y_k)^2\right],
  \label{eq:oracle}
\end{equation}
where $y_k$ is defined in \eqref{eq:bellman}.
% \textbf{We still may need to explain y in the formula with one sentence.}
A recently proposed, practically successful alternative approach
\citep{mnih2015,silver2016mastering} is to learn this
representation using an artificial deep neural-network model, leading to the
so-called \textit{deep Q-learning} family of methods which
This is the current state-of-the-art in RL research.
The set of model parameters $\theta$ that instantiate the non-linear interactions
between layers of the artifical neural network
may find a neurobiological correspondence in the adaptive strengths of axonal
connections between neurons from the different levels
of the neural processing hierarchy
\citep{mesulam1998sensation, taylor2015global}.
